
# Load libraries

```{r}
library(tidyverse)
library(here)
library(furrr)
library(magrittr)
library(janitor)
library(viridis)
```

# Read data

```{r}
input_data <- read.csv(file = here::here("data","export-gender-degree.csv"),
         header = TRUE)
```

Clean data

```{r}
input_data <- input_data %>% clean_names()
```

# Gender dependency for the occurrence of each degree  

Lump all degrees > 10 in one category

```{r}
input_data <- 
  input_data %>% 
    mutate(degree = as.double(degree)) %>% 
    mutate(degree_lumped = case_when(
    degree >= 10 ~ 11,
    TRUE ~ degree
))
```


Calculate statistics for female

```{r}
female <-
  input_data %>% filter(gender == "female")
```

Calculate statistics for female:

```{r}
female_degree <- 
  female %>% 
    group_by(degree_lumped) %>% 
    summarize(absolute = n(),
              relative_frequency = n()/nrow(female))
```

Add extra column to indicate gender:

```{r}
female_degree %<>% mutate(gender = "female")
```

Calculate statistics for male

```{r}
male <-
  input_data %>% filter(gender == "male")
```

Calculate statistics for male:

```{r}
male_degree <- 
  male %>% 
    group_by(degree_lumped) %>% 
    summarize(absolute = n(),
              relative_frequency = n()/nrow(male))
```

Add extra column to indicate gender:

```{r}
male_degree %<>% mutate(gender = "male")
```

Merge `male_degree` and `female_degree`

```{r}
gender_degree <- bind_rows(male_degree, female_degree)
```

Make `degree_lumped` a factor

```{r}
gender_degree %<>% mutate(degree_lumped = as.factor(degree_lumped))
```

Change `11` to `>10`

```{r}
gender_degree %<>% 
  mutate(degree_lumped = recode(degree_lumped,
    "11" = ">10"))
```


Visualization of absolute numbers:

```{r}
absolute <- ggplot(data = gender_degree, 
       aes(x = degree_lumped, y = absolute, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge(), colour = "black") +
  scale_fill_viridis_d() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        legend.title = element_blank(),
        legend.position = "none",
        axis.line = element_line(colour = "black"),
        axis.text=element_text(size=14),
        axis.title=element_text(size=16)
        ) +
  labs(y = "Total number of actors with \n a number of links", 
       x = "Number of links")
  

```


Visualization of relative numbers:

```{r}
relative <- ggplot(data = gender_degree, 
       aes(x = degree_lumped, y = relative_frequency, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge(), colour = "black") +
  scale_fill_viridis_d(name = "Gender") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(size=14),
        axis.title = element_text(size=16),
        legend.position = c(0.8, 0.8),
        legend.text = element_text(size=14),
        legend.title = element_text(size=14)

        ) +
  labs(y = "Relative number of actors with \n a number of links", 
       x = "Number of links") 
```

```{r}
myplot <- cowplot::plot_grid(absolute, relative)
```

