

# Load libraries

```{r}
library(tidyverse)
library(here)
library(janitor)
library(ggpubr)
library(lme4)
```

# Read and clean data

## Merge datafiles

```{r}
edge_file <- read.csv(file = here::here("data","weighted_combinations.csv"),
         header = TRUE,
         row.names = 1)
```


```{r}
node_file <- read.csv(file = here::here("data","export-gender-degree.csv"),
         header = TRUE)
```

Clean data

```{r}
node_file <- node_file %>% clean_names()
```

Merge dataframes for person 1:

```{r}
edge_file <-
  edge_file %>% 
    left_join(
      y = select(node_file, id, gender, nationality, date_of_birth, degree),  
      by = c("person_id_1" = "id"))
```


```{r}
names(edge_file)
```
Rename variables:

```{r}
edge_file <- 
  edge_file %>% rename(
   gender_1 = gender,
   nationality_1 = nationality,
   birth_1 = date_of_birth,
   degree_1 = degree)
```


Merge dataframes for person 2:

```{r}
edge_file <-
  edge_file %>% 
    left_join(
      y = select(node_file, id, gender, nationality, date_of_birth, degree),  
      by = c("person_id_2" = "id"))
```


```{r}
names(edge_file)
```
Rename variables:

```{r}
edge_file <- 
  edge_file %>% rename(
   gender_2 = gender,
   nationality_2 = nationality,
   birth_2 = date_of_birth,
   degree_2 = degree)
```

Rearrange columns:

```{r}
edge_file <- 
  edge_file %>% 
    select(person_id_1, person_id_2,
           records,
           degree_1, degree_2,
           gender_1, gender_2,
           nationality_1, nationality_2,
           birth_1, birth_2)
```



## Calculate variables

Remove all unknowns:

```{r}
# Gender

edge_file <- 
  edge_file %>% 
    filter(gender_1 != "unknown") %>% 
    filter(gender_2 != "unknown")

# Nationality

edge_file <- 
  edge_file %>% 
    filter(nationality_1 != "unknown") %>% 
    filter(nationality_2 != "unknown")

# Age difference

edge_file <- 
  edge_file %>% 
    filter(birth_1 != "S.D.") %>% 
    filter(birth_2 != "S.D.")

```

Extract year:

```{r}
edge_file <- 
  edge_file %>% 
    mutate(year_1 = substr(birth_1,1,4)) %>% 
    mutate(year_2 = substr(birth_2,1,4)) %>% 
  
  # From character to numeric
  
    mutate(year_1 = as.numeric(year_1)) %>% 
    mutate(year_2 = as.numeric(year_2)) 
```

Calculate independent variables:

```{r}
edge_file <- 
  edge_file %>% 
    mutate(gender_diff_01 = case_when(
      gender_1 == gender_2 ~ "0",
      gender_1 != gender_2 ~ "1"
    ))
```


```{r}
edge_file <- 
    edge_file %>% 
    mutate(gender_diff_MV = case_when(
        gender_1 == "female" & gender_2 == "female" ~ "FF",
        gender_1 == "male" & gender_2 == "male" ~ "MM",
        TRUE ~ "MF"
    ))
```


```{r}
# edge_file <- 
#  edge_file %>% 
#    mutate(nationality_diff = case_when(
#      nationality_1 == nationality_2 ~ "0",
#      nationality_1 != nationality_2 ~ "1"
#    ))
```

```{r}
edge_file <- edge_file %>% mutate(age_diff = abs(year_1 - year_2))
```

Remove all records for which the age difference is > 50 years

```{r}
edge_file <- 
  edge_file %>% filter(age_diff <= 50) %>% filter(records < 20000)
```

Calculate mean time_period:

```{r}
edge_file <- edge_file %>% mutate(time_period = purrr::map2_dbl(year_1,year_2,~mean(.x,.y)))
```


# Analyses

Generate plot

```{r}
myplot <- 
  ggplot(data = edge_file,
         aes(x = time_period, y = log(records), colour = gender_diff_MV)) +
    geom_point() +
    geom_smooth(method = "lm") +
    scale_color_viridis_d(
      labels = c("Female-female", "Female-male", "Male-male")) +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          axis.text=element_text(size=14),
          axis.title=element_text(size=16),
          legend.title = element_blank(),
          legend.text = element_text(size = 14)
          ) +
    labs(y = "Total number specimens collected \n (log scale)", 
         x = "Time period")
  
```

```{r}
absolute <- ggplot(data = gender_degree, 
       aes(x = degree_lumped, y = absolute, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge(), colour = "black") +
  scale_fill_viridis_d() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        legend.title = element_blank(),
        legend.position = "none",
        axis.line = element_line(colour = "black"),
        axis.text=element_text(size=14),
        axis.title=element_text(size=16)
        ) +
  labs(y = "Total number of actors with \n a number of links", 
       x = "Number of links")
  

```



```{r}
absolute <- ggplot(data = gender_degree, 
       aes(x = degree_lumped, y = absolute, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge(), colour = "black") +
  scale_fill_viridis_d() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        legend.title = element_blank(),
        legend.position = "none",
        axis.line = element_line(colour = "black"),
        axis.text=element_text(size=14),
        axis.title=element_text(size=16)
        ) +
  labs(y = "Total number of actors with \n a number of links", 
       x = "Number of links")
  

```


Inspect dependent variable:

```{r}
ggdensity(edge_file$records)
```

**MODEL 1 (preferred): Generalized mixed model using Inverse gamma distribution:**

```{r}
glmer(
  data = edge_file,
  records ~ time_period * gender_diff_MV +(1|person_id_1),
  family = Gamma("inverse")) %>% 
  summary()
```

**MODEL 2: Linear mixed model using normal distribution of log transformed dependent variable:**

```{r}
lmer(
  data = edge_file,
  log(records) ~ time_period * gender_diff_MV +(1|person_id_1)) %>% 
  anova()
```
**MODEL 3: Generalized linear model using poisson distribution:**

```{r}
glmer(
  data = edge_file,
  records ~ age_diff * gender_diff +(1|person_id_1),
  family = poisson) %>% 
  summary()
```
